### 2015-07-05 paper.tex
add rates of rock on diff E cut, and modify the sum rate

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates}
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Sum \\
			\hline
			E$>$0.7MeV &2.39   &2.43  &69.23  &0.89  &0.82 &15.94   &91.7  \\
			E$>$0.6MeV &4.26   &2.66  &75.26  &0.95  &0.94 &19.79   &103.86 \\
			E$>$0.5MeV &12.06  &2.83  &81.49  &0.98  &1.06 &23.36   &121.78 \\
			E$>$0.4MeV &13.86  &3.24  &87.84  &1.22  &1.29 &26.11   &133.56 \\
			E$>$0.3MeV &15.51  &3.72  &98.57  &1.57  &1.51 &31.60   &152.48 \\
			E$>$0.2MeV &17.16  &4.12  &117.33 &1.80  &1.89 &39.85   &182.15 \\
			E$>$0.1MeV &352.36 &5.27  &149.26 &2.22  &2.60 &54.97   &566.68 \\
			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}

>>>>

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates}
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Rock  &Sum \\
			\hline
			E$>$0.7MeV &2.39   &2.43  &69.23  &0.89  &0.82 &15.94 &7.42     &99.12   \\
			E$>$0.6MeV &4.26   &2.66  &75.26  &0.95  &0.94 &19.79 &8.1223   &111.982 \\
			E$>$0.5MeV &12.06  &2.83  &81.49  &0.98  &1.06 &23.36 &8.6414   &130.421 \\
			E$>$0.4MeV &13.86  &3.24  &87.84  &1.22  &1.29 &26.11 &9.89333  &143.453 \\
			E$>$0.3MeV &15.51  &3.72  &98.57  &1.57  &1.51 &31.60 &11.359   &163.839 \\
			E$>$0.2MeV &17.16  &4.12  &117.33 &1.80  &1.89 &39.85 &12.5804  &194.73  \\
			E$>$0.1MeV &352.36 &5.27  &149.26 &2.22  &2.60 &54.97 &16.0919  &582.772 \\
			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}
